---
title: "PGA Data"
date: "2/2/2019"
output: html_document
---

```{r libs, include=FALSE}
library(RCurl)
library(readxl)
library(dplyr)
library(openxlsx)
library(httr)
library(XML)
library(RCurl)
library(rvest)
library(janitor)
library(purrr)
library(stargazer)
```

```{r knitr-options, include = FALSE}
knitr::opts_chunk$set(fig.align="center",
                      warning = FALSE,
                      message = FALSE,
                      comment = NA)
```

## PGA Tour Web Scraper
The following creates a scraper to scrape the needed data from www.pgatour.com/stats. First the scaper is created, then the data for each year and stat is cleaned up and assigned to a corresponding variable. Finally, all stats for each player and year are merged into one data frame for each year. To use the function to get different stats for different years: get_all_data(stat, year) - where stat is corresponding stat number from website (ie. "127") and year is year of data desired (ie. 2018).

```{r}
## Create function to retrieve statistics from PGA website
get_all_data <- function(stat, year = 2018){
  pga_data_urls <- paste("https://www.pgatour.com/stats/stat.",
                       stat, ".",
                       year,
                       ".html",
                       sep = "")
  pg <- read_html(pga_data_urls)
  tables <- html_nodes(pg, "table")
  stat_data <- data.frame(html_table(tables))
  names(stat_data)[names(stat_data)=="X3"] <- "Year"
  stat_data[3] <- year
  return(stat_data)
}
```

##Get Ranking `ranking`
```{r}
rank_list <- lapply(2016:2019, get_all_data, stat="127")
rank_indx <- lengths(rank_list)
ranking_all <- as.data.frame(do.call(rbind,lapply(rank_list, `length<-`, max(rank_indx))))
ranking_all <- subset(ranking_all, select = c("Year", "PLAYER.NAME", "RANK.THIS.WEEK")) %>% clean_names() 
names(ranking_all)[names(ranking_all)=="rank_this_week"] <- "ranking"
```

## Get Top 10 Finishes and Wins `top_10` `wins`
```{r}
top10_list <- lapply(2016:2019, get_all_data, stat="138")
top10_indx <- lengths(top10_list)
top10_all <- as.data.frame(do.call(rbind,lapply(top10_list, `length<-`, max(top10_indx))))
top10_all <- subset(top10_all, select = c("Year", "PLAYER.NAME", "TOP.10", "X1ST")) %>% clean_names() 
names(top10_all)[names(top10_all)=="x1st"] <- "wins"
```

## Get Scoring Average & Rounds `score_average` `rounds`
```{r}
sa_list <- lapply(2016:2019, get_all_data, stat="120")
sa_indx <- lengths(sa_list)
score_avg_all <- as.data.frame(do.call(rbind,lapply(sa_list, `length<-`, max(sa_indx))))
score_avg_all <- subset(score_avg_all, select = c("Year", "PLAYER.NAME", "AVG", "ROUNDS")) %>% clean_names() 
names(score_avg_all)[names(score_avg_all)=="avg"] <- "score_average"
```

## Get Strokes Gained Stats `sg_total`
```{r}
sg_list <- lapply(2016:2019, get_all_data, stat="02675")
sg_indx <- lengths(sg_list)
strokes_gained_all <- as.data.frame(do.call(rbind,lapply(sg_list, `length<-`, max(sg_indx))))
tstrokes_gained_all <- subset(strokes_gained_all, select = c("Year", "PLAYER.NAME", "AVERAGE")) %>% clean_names() 
names(tstrokes_gained_all)[names(tstrokes_gained_all)=="average"] <- "sg_total"
```


## Get Driving Distance `driving_distance`
```{r}
d_list <- lapply(2016:2019, get_all_data, stat="101")
d_indx <- lengths(d_list)
driving_distance_all <- as.data.frame(do.call(rbind,lapply(d_list, `length<-`, max(d_indx))))
driving_distance_all <- subset(driving_distance_all, select = c("Year", "PLAYER.NAME", "AVG.")) %>% clean_names() 
names(driving_distance_all)[names(driving_distance_all)=="avg"] <- "driving_distance"
```

## Get Greens in Regulation (GIR) % `gir`
```{r}
gir_list <- lapply(2016:2019, get_all_data, stat="103")
gir_indx <- lengths(gir_list)
gir_all <- as.data.frame(do.call(rbind, lapply(gir_list, `length<-`, max(gir_indx))))
gir_all <- subset(gir_all, select = c("Year", "PLAYER.NAME", "X.")) %>%  clean_names()
names(gir_all)[names(gir_all)=="x"] <- "gir"
```

## Get average putts per round `putts_round`
```{r}
putts_list <- lapply(2016:2019, get_all_data, stat="119")
putts_indx <- lengths(putts_list)
putts_all <- as.data.frame(do.call(rbind, lapply(putts_list, `length<-`, max(putts_indx))))
putts_all <- subset(putts_all, select = c("Year", "PLAYER.NAME", "AVG")) %>%  clean_names()
names(putts_all)[names(putts_all)=="avg"] <- "putts_round"
```

## Get par 5 scoring average `par5_SA`
```{r}
five_list <- lapply(2016:2019, get_all_data, stat="144")
five_indx <- lengths(five_list)
five_all <- as.data.frame(do.call(rbind, lapply(five_list, `length<-`, max(five_indx))))
five_all <- subset(five_all, select = c("Year", "PLAYER.NAME", "AVG")) %>%  clean_names()
names(five_all)[names(five_all)=="avg"] <- "par5_SA"
```

## Get bounce back `bounce_back`
```{r}
bb_list <- lapply(2016:2019, get_all_data, stat="160")
bb_indx <- lengths(bb_list)
bb_all <- as.data.frame(do.call(rbind, lapply(bb_list, `length<-`, max(bb_indx))))
bb_all <- subset(bb_all, select = c("Year", "PLAYER.NAME", "X.")) %>%  clean_names()
names(bb_all)[names(bb_all)=="x"] <- "bounce_back"
```

## Get driving accuracy `driving_accuracy`
```{r}
da_list <- lapply(2016:2019, get_all_data, stat="102")
da_indx <- lengths(da_list)
da_all <- as.data.frame(do.call(rbind, lapply(da_list, `length<-`, max(da_indx))))
da_all <- subset(da_all, select = c("Year", "PLAYER.NAME", "X.")) %>%  clean_names()
names(da_all)[names(da_all)=="x"] <- "driving_accuracy"
```

## Get proximity to hole `hole_proximity`
```{r}
p_list <- lapply(2016:2019, get_all_data, stat="374")
p_indx <- lengths(p_list)
p_all <- as.data.frame(do.call(rbind, lapply(p_list, `length<-`, max(p_indx))))
p_all <- subset(p_all, select = c("Year", "PLAYER.NAME", "TOTAL.DISTANCE..FEET.")) %>%  clean_names()
names(p_all)[names(p_all)=="total_distance_feet"] <- "hole_proximity"
```

## Get scrambling % `scramble`
```{r}
s_list <- lapply(2016:2019, get_all_data, stat="130")
s_indx <- lengths(s_list)
s_all <- as.data.frame(do.call(rbind, lapply(s_list, `length<-`, max(s_indx))))
s_all <- subset(s_all, select = c("Year", "PLAYER.NAME", "X.")) %>%  clean_names()
names(s_all)[names(s_all)=="x"] <- "scramble"
```

## Get all PGA Players from years 2018:2020
```{r}
players <- as.data.frame(cbind(top10_all$player_name)) 
players <- (players[!duplicated(players),])
players <- as.data.frame(players)
names(players)[names(players)=="players"] <- "player_name"
```



## Merge all stats
```{r}
all_data <- left_join(ranking_all, top10_all, by =c("player_name", "year")) %>% 
  left_join(score_avg_all, by=c("player_name", "year")) %>% 
  left_join(bb_all, by=c("player_name", "year")) %>% 
  left_join(da_all, by=c("player_name", "year")) %>% 
  left_join(driving_distance_all, by=c("player_name", "year")) %>% 
  left_join(five_all, by=c("player_name", "year")) %>% 
  left_join(gir_all, by=c("player_name", "year")) %>% 
  left_join(p_all, by=c("player_name", "year")) %>% ## here
  left_join(putts_all, by=c("player_name", "year")) %>% 
  left_join(s_all, by=c("player_name", "year")) %>% 
  left_join(sg_t2g_all, by=c("player_name", "year")) %>% 
  left_join(tstrokes_gained_all, by=c("player_name", "year"))
all_data <- all_data[!(all_data$player_name=="Richard Johnson"),]
all_data <- all_data %>% arrange(player_name, year)
## Change NAs in wins and top 10 to 0 for binary
all_data$wins[is.na(all_data$wins)] <- 0
all_data$top_10[is.na(all_data$top_10)] <- 0
```

## Create csv file
```{r}
write.csv(all_data, file = "pga_all_data.csv") 
```

```{r}
all_data <- read.csv("pga_all_data3.csv")
all_data <- all_data[,-1]
```

```{r}
wgr_data <- read.csv("wgr_golf_rank.csv")
wgr_data <- wgr_data[,-1]
```

```{r}
pga_data <- left_join(all_data, wgr_data, by = c("player_name", "year"))
write.csv(pga_data, "pga_data_all.csv")
```